new_analses

### 2021-07-14 new_analyses.Rmd
MKN

@@

```{r}
biom %>%
  group_by(month) %>% 
  nest(-month) %>% 
  mutate(model = map(data, ~ lmer(log(biomass) ~ crop + 
                                 (1|year/location), data = .x)),
         anova = map(model, anova),
         emmeans = map(model, ~ emmeans(., ~ crop, 
                                        type = "response"))) -> analysis2
```

@@

```{r}
result2 %>% 
  filter(month == "First transplanting") %>% 
  ggplot(aes(x = crop, y = response,
             color = crop)) +
  geom_point(size = 2) +
  geom_linerange(aes(ymin = lower.CL, ymax = upper.CL)) +
  scale_color_manual(values = c(1,2,4,3,5, 1,3,2,4,5, 1,2,4,3,5)) +
  facet_grid(~ month, scales = "free") +
  coord_flip() +
  ylim(0, 30) +
  labs(y = expression(paste("Biomass (g plant "^"-1",")")), x = NULL) +
  theme_test() +
  theme(legend.position = "none") -> first

ggsave("figures/first_crop.png", width = 3)
```

```{r}
theme_set(theme_test(base_family = "roboto"))
result2 %>% 
  filter(month == "Second transplanting") %>% 
  ggplot(aes(x = crop, y = response,
             color = crop)) +
  geom_point(size = 2) +
  geom_linerange(aes(ymin = lower.CL, ymax = upper.CL)) +
  scale_color_manual(values = c(1,2,3,4,5, 1,4,2,3,5, 1,2,3,4,5)) +
  facet_grid(crop ~ month, scales = "free") +
  coord_flip() +
  labs(y = expression(paste("Biomass (g plant "^"-1",")")), x = NULL) +
  theme_test() +
  theme(legend.position = "none") -> second

ggsave("figures/second_crop.png", width = 3)
```

>>>>

```{r}
theme_set(theme_test(base_family = "roboto"))
result %>% 
  ggplot(aes(x = location, y = response,
             color = month)) +
  geom_point(size = 2, position = position_dodge2(width = 0.5)) +
  geom_linerange(aes(ymin = lower.CL, ymax = upper.CL),
                 position = position_dodge2(width = 0.5)) +
#  scale_color_manual(values = c(1,2,3,4,5, 1,4,2,3,5, 1,2,3,4,5)) +
  facet_grid(~ crop, scales = "free") +
  coord_flip() +
  labs(y = expression(paste("Biomass (g plant "^"-1",")")), x = NULL) +
  theme_test() +
  theme(legend.position = "bottom")

ggsave("figures/combined2.png", width = 6)
```

@@

```{r}
biom %>%
  unite("crop_yr", c("crop", "year"), sep = "-") %>% 
  filter(!is.na(weight)) %>% 
  group_by(month) %>% 
  nest(-month) %>% 
  mutate(model = map(data, ~ lmer(log(biomass) ~ crop_yr + 
                                 (1|location), data = .x)),
         anova = map(model, anova),
         emmeans = map(model, ~ emmeans(., ~ crop_yr, 
                                        type = "response"))) -> analysis2
```

@@

```{r}
result2 %>% 
  filter(month == "First transplanting") %>% 
  ggplot(aes(x = crop_yr, y = response,
             color = crop_yr)) +
  geom_point(size = 2) +
  geom_linerange(aes(ymin = lower.CL, ymax = upper.CL)) +
  scale_color_manual(values = c(1,2,4,3,5, 1,3,2,4,5, 1,2,4,3,5)) +
  facet_grid(~ month, scales = "free") +
  coord_flip() +
  ylim(0, 30) +
  labs(y = expression(paste("Biomass (g plant "^"-1",")")), x = NULL) +
  theme_test() +
  theme(legend.position = "none") -> first

ggsave("figures/first_crop.png")
```

```{r}
theme_set(theme_test(base_family = "roboto"))
result2 %>% 
  filter(month == "Second transplanting") %>% 
  ggplot(aes(x = crop_yr, y = response,
             color = crop_yr)) +
  geom_point(size = 2) +
  geom_linerange(aes(ymin = lower.CL, ymax = upper.CL)) +
  scale_color_manual(values = c(1,2,3,4,5, 1,4,2,3,5, 1,2,3,4,5)) +
  facet_grid(~ month, scales = "free") +
  coord_flip() +
  ylim(0, 20) +
  labs(y = expression(paste("Biomass (g plant "^"-1",")")), x = NULL) +
  theme_test() +
  theme(legend.position = "none") -> second

ggsave("figures/second_crop.png")
```
